The XQuery expressions of the XMark project are translated into NoSQL database queries based on the output result. In case of availability of secondary indexes, they have been created and utilized for efficient result.
 The following queries have some issues:
\begin{itemize}
\item Q4 and Q7 cannot be applied to NoSQL databases. These queries will be skipped during the measurement and analysis. In Q7, XPath  wild cards cannot be used in NoSQL databases, which makes it impossible to perform the query.

\item In Q14, full text search is measured in XQuery. MongoDB, Couchbase and RethinkDB do not support full text search, therefore the sub-string search is performed in these databases. 
\end{itemize}

\subsection{Queries in MongoDB}

In MongoDB, all the possible query methods are implemented to get the same result as XQuery. For simple queries, the \textit{find()} function is used. But for advanced queries, the aggregation pipeline and mapreduce are applied. The memory limit of the aggregation pipeline for a single stage is 100 MB, as mentioned in Section~\ref{mongo-query-model}. Enabling the \textit{allowDiskUse} option in aggregation pipeline allows to execute the query beyond the memory limit.
%For example, the \textit{find()} function can be used for Q1 to get result. As shown in  Code~\ref{mongo-xmark-q1}, the collection is filtered with default index \textit{\_id}  and the second parameter specifies the \textit{name} field to be retrieved.

MongoDB has no support for join queries. All the queries that need more than one collection  Q8, Q9, Q10, Q11 and Q12  are processed through the \textit{mongo shell}. Secondary indexes are created only when queries can be optimized. Without indexes, MongoDB has to scan every document in a collection to match the criteria of the query. The index is created by using \textit{createIndex} function as in Code~\ref{mongodb-create-index}. Some of the queries are explained here, full list of MongoDB queries and indexes is given in Appendix~\ref{mongodb-query-list}.

\begin{itemize}
\item \ref{mongodb-q-1} utilized the default index \textit{\_id}. The simple \textit{find()} function with  query criteria as first parameter and projection field  as second parameter in the collection \textit{people} returns the result.

\item In two queries \ref{mongodb-q-2} and \ref{mongodb-q-3},  the resulting items are wrapped up into new elements.  The sub-document \textit{bidder} has values of array type and contains numbers of bidders as objects in each element. Different operators in pipeline are used to process  arrays and objects to generate the output.

\item In \ref{mongodb-q-5}, a comparison operator \textit{\$gte}(greater than or equal to) is used to filter a collection and return the number of documents. This query can be optimized by a secondary index on the field \textit{price} of \textit{closed\_auctions} collection.  The \ref{mongodb-q-6} counts the number of documents in the collection \textit{regions}.

\item In \ref{mongodb-q-8}, the result is based on the join operation  between  \textit{people} and \textit{closed\_auction} collections.
The query iterates the \textit{people}  collections and counts the numbers of item bought by the person in \textit{closed\_auctions} collection.
The \textit{buyer.person} of \textit{closed\_auctions} is indexed for efficient filter in the \textit{\$match} operator of aggregation pipeline.   

 \item 
The  \ref{mongodb-q-9} has three collections \textit{regions}, \textit{people} and \textit{closed\_auctions}.  An index \ref{mongodb-i-8} of Q8 is utilized for \textit{closed\_auctions} and another index on fields \textit{regions} of \textit{regions} collection is created to filter item by region name that is also applicable to Q13. All three collections have to manually join in mongo shell.

\item The query \ref{mongodb-q-10} uses  \textit{categories} and \textit{people} collections to produce complex results with many new elements. The field \textit{profile.interest} of \textit{people} collection contains  arrays of categories is indexed that helps efficient search in arrays. 

%\item The\ref{mongodb-q-11} and \ref{mongodb-q-12} are value join queries between \textit{open\_auctions} and \textit{people} collection. The callback function \textit{forEach} of the MongoDB cursor in the \textit{people} collection calculated the result of the \textit{open\_auctions} collection and return the result.

\item The \textit{aggregate} function is used in \ref{mongodb-q-13} which utilized the index on field \textit{regions} of the \textit{regions} collection for the \$match operator. The output is returned in the new field \textit{item} with \textit{name} and \textit{description} of the item.

\item For \ref{mongodb-q-14} , a \textit{text index}[\ref{mongodb-i-7}] is created on collection \textit{regions}. The first parameter in \textit{createIndex} defines the field to be indexed and the second parameter is the name of the index. Text indexes can be applied on whole documents or on a perticular field whose value is a string or an array of string elements. The sub-document \textit{description} of collection \textit{regions} is an object, so the text index cannot be applied only to this field, but tp the whole documents of the \textit{regions} collection.  For query, simple \textit{find} function is implemented with query criteria. \textit{\$text} indicates that query is using text index and \textit{\$search} operator specifies a string to be search. 

\item Compared to the XQuery representations \ref{mongodb-q-15} and \ref{mongodb-q-16} are relatively complex in all NoSQL databases, including MongoDB, because the child axes original query needs to rewritten in various aggregation stages.
\item Query \ref{mongodb-q-17} is another simple query in MongoDB. The boolean operator \textit{\$exists} can filter the documents through the \textit{find} function and the projection parameter will select the field to be returned. 

\item The query \ref{mongodb-q-18} implements the user-defined function. In MongoDB, it is completed in two steps: a function is created and stored as document in the system collection \textit{system.js}. Afterwards, it is called through mapreduce. Table~\ref{tbl:mongodb-q18} illustrates Q18 by using mapreduce.
\item For \ref{mongodb-q-19}, the field  \textit{location} is indexed in collection \textit{regions} for sorting the data by location. The result is returned in new element \textit{item}.
\item
The final query \ref{mongodb-q-20} servs to calculate the aggregation. For this query, the Mapreduce is comparatively simpler than aggregation pipeline. For our benchmarking we have implemented Mapreduce. 
\end{itemize}
\begin{figure}
\centering
\begin{lstlisting}[language=JSON, caption=XMark Query Q1 in MongoDB, label=mongo-xmark-q1,basicstyle=\ttfamily\footnotesize]
		db.people.find({_id:"person0"},{_id:0,"name":1});
\end{lstlisting}
\centering
\begin{lstlisting}[language=JSON, caption=MongoDB secondary Index, label=mongodb-create-index,basicstyle=\ttfamily\footnotesize]
          db.closed_auctions.createIndex({regions:1})
\end{lstlisting}
\end{figure}


\begin{longtable}[hbt]{c|c}
    \caption{ User-defiend function \\and implementation in MongoDB(Q18)}
    \label{tbl:mongodb-q18}\\
    {function } & {map-reduce}\\
	\hline
\begin{minipage}{.3\textwidth}
\begin{lstlisting}[language=JSON,basicstyle=\ttfamily\footnotesize]
    db.system.js.save({ 
        "_id": "reserve", 
        "value": 
            function(a){ 
                return 2.20371*a; 
            } 
    })
\end{lstlisting}
\end{minipage} &
\begin{minipage}{.4\textwidth}
\begin{lstlisting}[language=JSON,basicstyle=\ttfamily\footnotesize]
db.open_auctions.mapReduce(
    function() {
       if(this.reserve){
        emit(this._id, reserve(this.reserve));
       }    
    },
    function(key,values) {
        return Array.sum(values);
    },
    { "out": { "inline": 1 } }
 );
\end{lstlisting}
\end{minipage}
\end{longtable}


\subsection{Queries in Couchbase}
Views are the query interface in Couchbase. The output of the views are queried through the SDKs to get the result. Each query except join queries consists of one view. The \textit{doctype} should be checked before \textit{emit} in \textit{map} function. Multiple views can be stored in a \textit{design document} and it is recommended to have few number of views in a single design document. There can be any numbers of design documents. For benchmarking, three design documents are created for all the queries. Q1-Q7 are stored in the first, the join queries Q8-Q12 views in second and remaining views in the third document design. 
\par
We have different buckets for each database instance. The views in development mode takes the subset of documents to create the sample index. In production mode all documents are used to create the full index of the view  as illustrated in Figure~\ref{fig:cb-views-workflow}. These indexes affect the performance because each bucket has its own RAM quota and the in-memory nature of Couchbase. At the time of measurements, the production mode views of other buckets are dropped so that enough memory can be assigned to that specific bucket. 
\par 
To query the views, different query options like \textit{limit}, \textit{group\_level}, \textit{key}, \textit{keys}, \textit{skip}, etc can be used get required result. The \textit{group\_level} options in query controls whether the reduce function reduces to a set of distinct keys or to a single result row.  \textit{descending} changes the direction of search by key in results. These two query options are most frequently used in our benchmarking queries.
\par
All XMark queries  are queried and evaluated through Node.js. The full list of Couchbase Mapreduce can be found in Appendix~\ref{couchbase-query-list}. Some of the important queries are explained here:


 \begin{itemize}
 \item  In \ref{cb-q-1}, the map function filters the documents by \textit{doctype} and the \textit{id} returns the required field by calling it in \textit{emit} function.
 
 \item \ref{cb-q-2} and \ref{cb-q-3} are deep arrays and objects processing queries like other NoSQL databases. In the map,  JavaScript is applied  to find the required elements in objects or arrays.
 
 \item Both queries \ref{cb-q-5} and \ref{cb-q-6} use the built-in \textit{\_count} function  in the reduce section.  In Q5, the map emits only when the condition matches with \textit{price} field of \textit{open\_auctions}, whereas for Q6, the map
 emits all the \textit{id} of \textit{regions} \textit{doctype}.  The \textit{\_count} function in reduce counts the numbers of emitted items. 
 \item The join operation in Couchbase is a bit complicated compared to other NoSQL databases. Each \textit{doctype} should have at least a view but it can be also used for other queries. In the case of \ref{cb-q-11} and \ref{cb-q-12}, the view on \textit{open\_auctions} can be used for both queries. The \ref{cb-q-8} contains two views: the first view selects the \textit{id} and \textit{name} field of \textit{people}. The second view aggregates \textit{doctype} \textit{closed\_auctions} by using the reduce function the with query option \textit{group\_level=1}. Finally, both views are joined using Node.js. 
 
 \item In \ref{cb-q-10}, two views on \textit{people}  are joined to get the results. Table~\ref{tbl:couchbase-q10-a} illustrate the view \textit{people\_interest} for Q10. At map phase, all the \textit{category} as key and  document key \textit{id} as value are emitted. In reduce, a custom reduce function groups the values by key. The query defines the grouping level which is 1 for this view that indicates the key. This view generates  \textit{people}'s \textit{id} group by interest category. Another view \textit{people\_profile} emits the \textit{id} as key and formatted profile of \textit{people} as values. The view \textit{people\_interest}  is joined to \textit{people\_profile} to get formatted result.
 \begin{longtable}[hbt]{c|c|c}
	\caption{ view \textit{person\_interest} in doctype \textit{people} for Q10}
	\label{tbl:couchbase-q10-a}\\
    {map} & {reduce} & {query}\\
	\hline
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JSON,basicstyle =\scriptsize]
function (doc, meta) {
      if(doc.doctype && doc.doctype=="people" 
      && doc.profile && doc.profile.interest){
        var interest = doc.profile.interest;
            for(i=0; i < interest.length; i++) {
          if(interest[i] && interest[i].category) {
            emit(interest[i].category, meta.id) 
          }
        }
      }
    }
\end{lstlisting}
\end{minipage} &
\begin{minipage}{.3\textwidth}
\begin{lstlisting}[language=JSON,basicstyle =\scriptsize]
 function(keys, values, rereduce) {
  return values
}
\end{lstlisting}
\end{minipage} &
\begin{minipage}{.15\textwidth}
\begin{lstlisting}[language=JSON,basicstyle =\scriptsize]
     group_level
            = 1
\end{lstlisting}
\end{minipage}
\end{longtable}

%\item For \ref{cb-q-11} and \ref{cb-q-12}, a common view in \textit{open\_auctions} is joined to two different views in \textit{people} for each query.

 %\item In \ref{cb-q-14} , the \textit{description} field in \textit{regions} is converted into string  that makes substring search possible.  The \ref{cb-q-15} and \ref{cb-q-16} are deep child axes queries. 
 
 \item A view in the \textit{regions} documents created for \ref{cb-q-19}. The map emits the \textit{location} as key and a JSON object as values.  A query  \textit{descending=false}  returns the resulting values in ascending order. 
 
 \item The final query \ref{cb-q-20} is given in Table~\ref{tbl:couchbase-q20}. In the map function, the document is emitted according to their class-name as key  and a counter value. In reduce, the \textit{\_sum} function sums all the counter values group by key as query \textit{group\_level=1}.
 \end{itemize}

\newpage
\begin{longtable}[hbt]{c|c|c}
	\caption{ XMark query Q20 in Couchbase Server}
	\label{tbl:couchbase-q20}\\
    {map} & {reduce} & {query}\\
	\hline
\begin{minipage}{.5\textwidth}
\begin{lstlisting}[language=JSON,basicstyle=\ttfamily\footnotesize]
function (doc, meta) {
    if(doc.doctype=="people"){
      var income = (doc.profile && doc.profile.income) ? 
                doc.profile.income : 0;
      if(income >= 100000 ){
    	 emit("preferred",1);
      }else if(income < 100000 && 
               income >= 30000) {
        emit("standard",1);
      }else if(income < 30000 &&
           income > 0 ){
       
        emit("challenge",1);
      } else {
       emit("na",1);
      }
    }
  }
\end{lstlisting}
\end{minipage} &
\begin{minipage}{.15\textwidth}
\begin{lstlisting}[language=JSON,basicstyle=\ttfamily\footnotesize]
     _sum
\end{lstlisting}
\end{minipage} &
\begin{minipage}{.2\textwidth}
\begin{lstlisting}[language=JSON,basicstyle=\ttfamily\footnotesize]
     group_level=1
\end{lstlisting}
\end{minipage}
\end{longtable}

\subsection{Queries in RethinkDB}

In RethinkDB, the performance of a read query can be improved through the secondary indexes. For XMark queries,  wherever possible, these indexes are utilized. The index has to be defined in the query and can only be used in one of the four functions \textit{getAll()}, \textit{between()}, \textit{eqJoin()} and \textit{orderBy()}. Table~\ref{tbl:rethinkdb-index-query} illustrates an example of creating a secondary index and its usage in a query.
\begin{longtable}{c|c}
	\caption{ RethinkDB secondary index and Query for Q13}
	\label{tbl:rethinkdb-index-query}\\
    {Index} & {Query}\\
	\hline
\begin{minipage}{.3\textwidth}
\begin{lstlisting}[language=JSON,basicstyle=\ttfamily\footnotesize]
    r.table("regions")
        .indexCreate("regions")
\end{lstlisting}
\end{minipage} &
\begin{minipage}{.5\textwidth}
\begin{lstlisting}[language=JSON,basicstyle=\ttfamily\footnotesize]
r.table("regions")
.getAll("australia",{index:"regions"})
    .map({  
       item:{  
          name:r.row("name"),
          description:r.row("description")
       }
    })
\end{lstlisting}
\end{minipage}
\end{longtable}
The full list of RethinkDB queries and indexes is given in Appendix~\ref{rethinkdb-query-list}. 
Some of the important queries in RethinkDB are explained here.

\begin{itemize}
\item  In \ref{rethink-q-1}, the \textit{get} function retrieves a document by its primary key from the \textit{people} table and selects the field \textit{name}.   

\item  The \textit{lamda} function of ReQL is one of the most powerful features among NoSQL databases to process the arrays and objects. This function is implemented in  queries \ref{rethink-q-2} and \ref{rethink-q-3} to filter and format the results. 

\item 
 In queries \ref{rethink-q-5} and \ref{rethink-q-6}, the \textit{count} function is implemented in a table. 
  \item Due to native support for joins between tables, join queries in RethinkDB are simpler compare to other NoSQL databases. An index \textit{buyer\_person} is created in the field "buyer.person" of \textit{closed\_auctions} table is created for \ref{rethink-q-8} and \ref{rethink-q-9}. In Q8, the \textit{map} function is implemented to joins two tables.

\end{itemize}

%\textit{closed\_auctions} table for Q8. Similarly, the Q9 can be improved by creating indexes in the tables \textit{regions} and \textit{closed\_auctions}. Other queries like Q13 and Q19 is also evaluated using indexes. For substring search in Q14, the value of  field \textit{description} is converted into text and then it is matched for the sub-string. All the queries and indexes are used for RethinkDB is given in ~\ref{rethinkdb-query-list}.
